---
title: "Table Display"
author: "Zeyu Li"
date: "June 6, 2015"
output: html_document
runtime: shiny
---
```{r, echo=FALSE}
```

### Data
<p>The data is from the paper “Getting What You Pay For: The Debate Over Equity in Public School Expenditures” by Deborah Lynn Guber (1999) from the Journal of Statistics Education.</p>

<p>There are a number of variables listed in the data description collected from 1994-1995 from public elementary and secondary schools:</p>

</p>
<dl>
  <dt>Expenditure</dt>
  <dd>- Expenditure per pupil in average daily attendance (in thousands of U.S. dollars) </dd>
  <dt>Teacher Salary</dt>
  <dd>- Estimated average annual salary of teachers (in thousands of US dollars)          </dd>
  <dt>Fraction </dt>
  <dd>- Percentage of all eligible students taking the SAT
  </dd>
  <dt>Scores </dt>
  <dd>- State average
  </dd>
</dl>
</p>

<p>Just a glance at the data: </p>
```{r, echo=FALSE}
shinyAppDir(appDir = "show_data_app/", options = list(
    width="100%", height=350
  ))
```

<p>As we can see, there are 50 observation points representing each state with the various data recorded in each of them.</p>




