---
title: "Scatterplot"
author: "Zeyu Li"
date: "June 6, 2015"
output: html_document
runtime: shiny
---
```{r, echo=FALSE}
setwd("~/Dropbox/Senior_Research/Stat_Summer15_Research/DynDocs/SAT/individual_shiny_apps/shiny_reactivity_test")
```

## Data Analysis

### Correlation and Causation

<p>Correlation is the relationship between two different variables. When two variables are positively correlated, they have a positive association with each other; that is, when there is more of one variable, there is more of the other. For example, there might be more hot chocolate sales during colder weather and more iced tea sales during hot weather. When two things are negatively correlated with each other, they will have a negative association with each other. For example, when people have more money, they might be less inclined to purchase off-brand goods (such examples are known as inferior goods in economics).</p> 

<p>It is important to note that correlation does not equal causation. That is, just because two variables move together well does not mean that one causes the other variable to increase. For example, if an epidemic spreads in certain parts of the world, higher numbers of doctors in those places with high incidences of a disease does not mean that the doctors caused the disease. Rather, doctors might have been sent to those places to address it.</p>

<p>When using an explanatory variable, which is the variable that we consider that might affect the variable of interest (i.e. the independent variable), we need to make sure that the explanatory variable is not really just showing the effect of another variable. Often, explanatory variables will have a number of other variables that are correlated with them, which can skew the explanatory power of the observations.</p>

<p>We see a negative correlation between sat scores and teacher salary:</p>

```{r, echo=FALSE}
library(shiny)
runApp("my_app2/")
```




